---
title: "R ggplot2 Plot Examples Notebook"
output: 
  html_notebook: 
    toc: yes
    toc_depth: 4
---


# R ggplot2 Plot Examples

> [ggplot2-gyakubiki-book](https://kazutan.github.io/ggplot2-gyakubiki-book/Plotting_two_variables.html)

## 1. Plotting_two_variables

```{r Plotting_two_variables, echo=TRUE}
# Load ggplot2 package
if(!suppressWarnings(require(ggplot2)))
{
    install.packages('ggplot2')
    require("ggplot2")
}

# data
test_data <- data.frame(
  var0 = 100 + c(0, cumsum(runif(49, -20, 20))),
  var1 = 150 + c(0, cumsum(runif(49, -10, 10))),
  date = seq.Date(as.Date("2002-01-01"), by="1 month", length.out=100))
str(test_data)
# 'data.frame':	100 obs. of  3 variables:
#  $ var0: num  100 116 129 132 129 ...
#  $ var1: num  150 150 157 151 154 ...
#  $ date: Date, format:  ...

head(test_data, 5);tail(test_data, 5);

# use wide format data to draw plot
p1 <- ggplot(test_data, aes(date)) +
  geom_line(aes(y = var0, colour = "var0")) +
  geom_line(aes(y = var1, colour = "var1"))

p1

test_data_long <- reshape2::melt(test_data,id.vars = c("date"),
  variable.name = "variable", 
  value.name = "value")
#         date variable     value
# 1 2002-01-01     var0 100.00000
# 2 2002-02-01     var0 112.84507
# 3 2002-03-01     var0 115.37682
# 4 2002-04-01     var0 108.17863
# 5 2002-05-01     var0  99.08404
# 6 2002-06-01     var0 107.86098

# use long format data to draw plot
p2 <- ggplot(data=test_data_long, aes(x=date, y=value, colour=variable)) +
  geom_line()

p2
```

## 2. Showing_data_values_on_stacked_bar

```{r Showing_data_values_on_stacked_bar}
Year <- c(rep(c("2006-07", "2007-08", "2008-09", "2009-10"
), each = 4))

Category <- c(rep(c("A", "B", "C", "D"), times = 4))

Frequency <- c(168,  259,  226,  340,  216,  431,  319,  368,  423,  645,  234,  685,  166,  467,  274,  251)

Data <- data.frame(Year, Category, Frequency)

str(Data)

require(ggplot2)

p <- ggplot(Data, aes(Year, Frequency, fill = Category)) +
    geom_bar(stat = "identity") +
    theme_bw()

p + geom_text(aes(label = Frequency),
    size = 3,
    hjust = 0.5,
    vjust = 3,
    position = "stack") 

## method2
library(plyr)
library(ggplot2)

# calculate midpoints of bars (simplified using comment by @DWin)
Data <- ddply(Data, .(Year), transform, pos = cumsum(Frequency) - (0.5 * Frequency))

# plot bars and add text
p <- ggplot(Data, aes(x = Year, y = Frequency)) +
     geom_bar(aes(fill = Category), stat="identity") +
     geom_text(aes(label = Frequency, y = pos), size = 3)
p

## method 3
library(plyr)
library(ggplot2)
Year      <- c(rep(c("2006-07", "2007-08", "2008-09", "2009-10"), each = 4))
Category  <- c(rep(c("A", "B", "C", "D"), times = 4))
Frequency <- c(168, 259, 226, 340, 216, 431, 319, 368, 423, 645, 234, 685, 166, 467, 274, 251)
Data      <- data.frame(Year, Category, Frequency)

# calculate midpoints of bars (simplified using comment by @DWin)
Data <- ddply(Data, .(Year), transform, pos = cumsum(Frequency) - (0.5 * Frequency))

# plot bars and add text
p <- ggplot(Data, aes(x = Year, y = Frequency)) +
     geom_bar(aes(fill = Category), stat="identity") +
     geom_text(aes(label = Frequency, y = pos), size = 3)
p

## method 4
p <- ggplot(Data, aes(x = Year, y = Frequency)) +
  geom_bar(aes(fill = Category), stat="identity") +
  geom_text(aes(label = Frequency), size = 3, position = "stack", vjust = Frequency/75)
p

```

## 3. ggplot2 font

```{r font for ggplot2}
font_A <- "Consolas"
font_B <- "Courier"
font_C <- "Courier New"
font_D <- "宋体"
font_E <- "楷体"
font_F <- "隶书"
font_G <- "黑体"

library(ggplot2)

d <- data.frame(X=rep(1:5, 2), Y=c(1:5, 5:1), A=rep(c('a','b'), each=5))

ggplot(data=d, aes(x=X, y=Y, group=A, color=A)) +
  geom_line(size=2) +
  labs(x="你是X", y="你是Y", color="blue", title="测试字体Font") + 
  theme(text = element_text(family = font_F))

ggplot(data=d, aes(x=X, y=Y, group=A, color=A))+
  geom_line(size=2) +
  labs(x="你是X", y="你是Y", color="blue", title="测试字体Font") + 
  theme(text = element_text(family = font_A),  #all
        title = element_text(family = font_B),  #title
        axis.title = element_text(family = font_A),  #axis.title 
        axis.title.x = element_text(family = font_B),  #axis.title.x
        axis.text = element_text(family = font_A),  #axis.text
        axis.text.y = element_text(family = font_B),  #axis.text.y
        legend.text = element_text(family = font_A),  #legend.text
        legend.title = element_text(family = font_B),  #legend.title
        plot.title = element_text(family = font_A)  #plot.title
        ) 

```

## 4. adding_space_between_bars_in_ggplot2

```{r adding_space_between_bars_in_ggplot2}
library(ggplot2)

Treatment <- rep(c('T','C'),each=2)
Gender <- rep(c('M','F'),2)
Response <- sample(1:100,4)
df <- data.frame(Treatment, Gender, Response)

hist <- ggplot(df, aes(x=Gender, y=Response, fill=Treatment))
hist + geom_bar(position = "dodge", stat = "identity") + scale_y_continuous(limits = c(0, 
    100), name = "") 

# adding_space_between_bars_in_ggplot2
hist + geom_bar(width = 0.4, position = position_dodge(width = 0.5))


plot <- ggplot(df, aes(x=Gender, y=Response, fill=Treatment)) + 
  scale_y_continuous(limits = c(0, 100), name = "") +
  theme(legend.position = "none") +
  facet_wrap(~p) +
  mapply(function(w, pw)
    geom_bar(data = transform(df, p=sprintf("w_%.02f_pw_%.02f", w, pw)), stat = "identity", width= w, position = position_dodge(width = pw)),
    w = c(0.6,0.6,0.6,0.3,0.3,0.3), pw = c(0.4,0.7,1.0,0.4,0.7,1.0))
plot

# error bar
ggplot(mtcars, aes(factor(cyl), mpg, fill = factor(am))) + 
  stat_summary(fun.data = mean_se, position = position_dodge(width = 0.9), geom = "linerange") +
  stat_summary(fun.y = mean, geom = "bar", position = position_dodge(width = 0.9))

# error bar2
ggplot(mtcars, aes(factor(cyl), mpg, fill = factor(am))) + 
  stat_summary(fun.data = mean_se, position = position_dodge(width = 0.8), geom = "linerange") +
  layer(geom = "bar", params = list(width = 0.6, fun.data = mean_se), stat = "summary", 
        position = position_dodge(width = 0.8))

```

## 5. bandgraph_ggplot2

```{r bandgraph_ggplot2}
library(ggplot2)
p <- ggplot(mtcars, aes(x = as.factor(gear), fill = as.factor(vs))) +
  geom_bar()
p

# position = fill
p <- ggplot(mtcars, aes(x = as.factor(gear), fill = as.factor(vs))) +
  geom_bar(position = "fill")
p

# scale_y_continuous(labels=percent)
require(scales)
p <- ggplot(mtcars, aes(x = as.factor(gear), fill = as.factor(vs))) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = percent)
p

# transfer X as Y
require(scales)
p <- ggplot(mtcars, aes(x = as.factor(gear), fill = as.factor(vs))) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = percent) +
  coord_flip()
p

# transfer X as Y 2
require(scales)
mtcars.v2 <- transform(mtcars, gear2 = gear * -1)
p <- ggplot(mtcars.v2, aes(x = reorder(gear, gear2), fill = as.factor(vs))) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = percent) +
  coord_flip()
p

```

## 6. flipped_cartesian_coordinates

```{r flipped_cartesian_coordinates}
library(ggplot2)

ggplot(mtcars, aes(x = as.factor(gear))) +
  geom_bar()

# coord_flip() x as y
ggplot(mtcars, aes(x = as.factor(gear))) +
  geom_bar() +
  coord_flip()

# ylim
ggplot(mtcars, aes(x = as.factor(gear))) +
  geom_bar() +
  coord_flip() +
  ylim(c(0,20))

# reorder
ggplot(mtcars, aes(x = reorder(as.factor(gear), gear * -1))) +
  geom_bar() +
  coord_flip()

# reorder/reverse
ggplot(mtcars, aes(x = gear)) +
  geom_bar() +
  coord_flip() +
  scale_x_reverse()

```

## 7. ggplot2_element_function
```{r ggplot2_element_function}
require(ggplot2)

# add vline
p <- ggplot(aes(x = mpg, y = hp), data = mtcars)
p + geom_vline(xintercept = 20) + geom_point(data = mtcars)


myFunction <- function() {
  return(
    geom_vline(xintercept = 20) + geom_point(data = mtcars)
  )
}
p <- ggplot(aes(x = mpg, y = hp), data = mtcars)
p
# p + myFunction()
# p + myFunction()


# add vline
myFunction <- function()
 list(geom_vline(xintercept = 20),
      geom_point(data = mtcars))

p <- ggplot(aes(x = mpg, y = hp), data = mtcars)
p + myFunction()


# error bar、se
lay = list(stat_summary(fun.y = mean, geom = "line"),
           stat_summary(fun.data = mean_se))

ggplot(mtcars, aes(am, mpg, colour = factor(vs), group=factor(vs))) + lay

ggplot(iris, aes(Species, Sepal.Length, group=1)) + lay


## 

p <- ggplot(iris, aes(y=Sepal.Width, x=Species)) +
  stat_summary(fun.y=mean, geom = "bar") + 
  ylim(0,6) + 
  lapply(1:3, function(i) geom_segment(x=i-0.4, y=7-i, xend=i+0.4, yend=7-i))
p

##
p = ggplot(data.frame(x = c(-10, 10)), aes(x)) +
  mapply(function(m, s, co) stat_function(fun = dnorm, args = list(mean = m, sd = s), colour = co), 
         -1:1, c(0.5, 1, 1.5), rainbow(3))
p

```

## 8. set_only_lower_bound
```{r set_only_lower_bound}

library(ggplot2)
ggplot(mtcars, aes(wt, mpg)) +
  geom_point()

# scale_y_continuous
ggplot(mtcars, aes(wt, mpg)) +
  geom_point() + 
  scale_y_continuous(limits = c(0, NA))

#
ggplot(mtcars, aes(wt, mpg)) +
  geom_point() + 
  ylim(c(0, NA)) +
  xlim(c(-2, NA))

#

ggplot(mtcars, aes(wt, mpg)) +
  geom_point() + 
  expand_limits(y=0)

```

## 9. sort_legend_in_ggplot2
```{r sort_legend_in_ggplot2}

require(ggplot2)
p <- ggplot(diamonds, aes(cut, fill = clarity)) + 
  geom_bar()
p

#guides
p <- ggplot(diamonds, aes(cut, fill = clarity)) + 
  geom_bar() +
  guides(fill = guide_legend(reverse = TRUE))
p

#fill，guide_legend
p <- ggplot(diamonds, aes(cut, colour = clarity)) + 
  geom_bar(fill = "white") +
  guides(colour = guide_legend(reverse = TRUE))
p

#
p <- ggplot(diamonds, aes(carat, price, colour = clarity, shape = cut)) +
  geom_point() +
  theme(legend.position = "top")
p

#guide_legend

p <- ggplot(diamonds, aes(carat, price, colour = clarity, shape = cut)) +
  geom_point() +
  theme(legend.position = "top") +
  guides(shape = guide_legend(order = 2),
         colour = guide_legend(order = 1))
p

#
p + guides(shape = guide_legend(order = 1),
         colour = guide_legend(order = 2))

#
p <- ggplot(iris, aes(x = Species, y = Sepal.Length, colour = Sepal.Width)) + 
  geom_point()
p

#
p <- ggplot(iris, aes(x = Species, y = Sepal.Length, colour = Sepal.Width)) + 
  geom_point() +
  guides(colour = guide_colourbar(reverse = TRUE))
p

#
p <- ggplot(diamonds, aes(carat, price, colour = depth, shape = cut)) +
  geom_point() +
  theme(legend.position = "top") +
  guides(shape = guide_legend(order = 1),
         colour = guide_colourbar(order = 2))
p

```

## 10. sort_x-axis
```{r sort_x-axis}
library(ggplot2)

p <- ggplot(mtcars, aes(x = gear, y = wt)) + 
  geom_point()
p

# revert x
p <- ggplot(mtcars, aes(x = gear, y = wt)) + 
  geom_point() +
  scale_x_reverse()
p

#box plot
p <- ggplot(mtcars, aes(x = as.factor(gear), y = wt)) +
  geom_boxplot()
p

#transform
mtcars.v2 <- transform(mtcars, gear2 = gear * -1) # 値の順序が逆転する変数gear2を作成
p <- ggplot(mtcars.v2, aes(x = reorder(gear, gear2), y = wt)) +
  geom_boxplot()
p

# factor
ggplot(iris, aes(x = Species, y = Sepal.Width)) +
  stat_summary(fun.y = mean, geom = "bar")

#reorder
ggplot(iris, aes(x = reorder(x = Species, X = Sepal.Width, FUN = mean), y = Sepal.Width)) +
  stat_summary(fun.y = mean, geom = "bar")
```

## 11. spline_ggplot2
```{r spline_ggplot2}

# geom_smooth(aes(x=(spline(y~x)$x, y=spline(y~x)$y))
library(ggplot2)
n <- 10
d <- data.frame(x = 1:n, y = rnorm(n))
ggplot(d,aes(x,y)) + geom_point() + 
  geom_line(data=data.frame(spline(d, n=n*10)))

```

## 11. transparent_bg_using_ggplot2
```{r transparent_bg_using_ggplot2}
d <- rnorm(100) #data

# transparent
png('tr_tst1.png',width=300,height=300,units="px",bg = "transparent")
boxplot(d)
dev.off()

# ggplot2 plot
df <- data.frame(y=d,x=1)
p <- ggplot(df) + stat_boxplot(aes(x=x,y=y)) 
p <- p + theme(
    panel.background = element_rect(fill = "transparent",color = NA),
    panel.grid.minor = element_line(color = NA), 
    panel.grid.major = element_line(color = NA)
)
# save png
png('tr_tst2.png',width=300,height=300,units="px",bg = "transparent")
p
dev.off()
```

### use theme to set transparent
```{r transparent}
d <- rnorm(100)
df <- data.frame(y=d,x=1)
p <- ggplot(df) + stat_boxplot(aes(x = x,y=y)) 
p <- p + theme(
    panel.background = element_rect(fill = "transparent",color = NA),
    panel.grid.minor = element_line(color = NA), 
    panel.grid.major = element_line(color = NA),
    plot.background = element_rect(fill = "transparent",color = NA)  # add
)
p
```

### use ggsave
```{r ggsave}
ggsave("tr_tst3.png", p, bg = "transparent")
sessionInfo()

require(ggthemes)
p + theme_wsj()
```

## 12. other

```{r other}
f <- data.frame(x=c(x1,x2,x3), y=rep(y,3), type=rep(LETTERS[1:3], each=length(y)))

p
```







