---
title: "tidyverse_readxl"
author: "Stone_Hou"
date: '`r Sys.Date()`'
output:
  html_notebook:
    number_sections: yes
    theme: readable
    toc: yes
    toc_depth: 4
  html_document:
    toc: yes
    toc_depth: '4'
---

# tidyverse_readxl

## Load library(readxl) package

```{r Load package}
# ?rm()
rm(list=ls())
# Load data.table package
if(!suppressWarnings(require(readxl)))
{
    install.packages('readxl')
    require('readxl')
}

?readxl
```

## Load Data--明确文件内表单

```{r}
excel_sheets('mydata.xlsx')
# [1] "Sheet1"     "Sheet2"     "TestSheet3"
```

## read_excel()表单数据读取

col_names表示是否以第一行作为变量名，可以给出一个向量自定义列名。

sheet如果不声明的话，就默认读取第一张表单。

read_excel自行截取最小的能够囊括所有观测值的矩阵范围进行读取，所以不用太担心各行变量列数不同而没有读取完整数据。

`readxl::read_excel()` will guess column types, by default, or you can provide them explicitly via the `col_types` argument. The `col_types` argument is more flexible than you might think; you can mix actual types in with `"skip"` and `"guess"` and a single type will be recycled to the necessary length.

Here are different ways this might look:

```{r}
read_excel("yo.xlsx")
read_excel("yo.xlsx", col_types = "numeric")
read_excel("yo.xlsx", col_types = c("date", "skip", "guess", "numeric"))

read_excel("yo.xlsx", skip = 5)
read_excel("yo.xlsx", n_max = 100)
read_excel("yo.xlsx", skip = 5, n_max = 100)
read_excel("yo.xlsx", range = "C1:E7")
read_excel("yo.xlsx", range = cell_rows(6:23))
read_excel("yo.xlsx", range = cell_cols("B:D"))
read_excel("yo.xlsx", range = anchored("C4", dim = c(3, 2)))



f <- read_excel('mydata.xlsx', sheet = "Sheet2", col_names = F)
View(f)

# 如果想要读取选定的范围的数据，则可以在range里声明。
# 比如只读取第一张表单中的前三行前四列的数据：

(f <- read_excel(
  'mydata.xlsx',
  sheet = "Sheet2",
  col_names = F,
  range = 'B2:F8'
  ))
View(f)

read_excel(readxl_example("deaths.xlsx"), range = cell_rows(5:15))

read_excel(
  readxl_example("deaths.xlsx"),
  range = cell_rows(5:15),
  col_types = c("guess", "skip", "guess", "skip", "skip", "skip")
)

(clippy <- 
   read_excel(readxl_example("clippy.xlsx"), col_types = c("text", "list")))

```

## Vignettes from package 'readxl'